The Cluster Difference Imaging Photometric Survey (CDIPS). I. Light Curves \& Planet Candidates in Open Clusters from TESS Sectors 6 \& 7

### 2019-06-12 paper/ms.tex
update the figs

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{sector6_cluster_field_star_positions.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Celestial positions of light curves from Sector 6}
        \label{fig:lcradecsector6}
    }
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the updated figures from \citet{vanderspek_2018}.
  The noise from unresolved background stars is expected to be more
  important than read noise at the faint end, but is omitted from the
  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}

>>>>

\begin{figure}[t]
    \begin{center}
        \leavevmode
        \includegraphics[width=0.49\textwidth]{cluster_field_star_positions.png}
    \end{center}
    \vspace{-0.5cm}
    \caption{
        {\bf Celestial positions of light curves from Sectors 6 and 7.}
        \label{fig:lcradecsector6}
    }
\end{figure}

@@

\begin{figure}[t]
	\begin{center}
		\leavevmode
		\includegraphics[width=0.49\textwidth]{rms_vs_mag.png}
	\end{center}
	\vspace{-0.5cm}
  \caption{ {\bf Standard deviation vs catalog TESS-band magnitude for
  trend-filtered CDIPS light curves.} The minimum RMS across all three
  aperture sizes was selected.  The photon and read noise are
  calculated using the effective area from \citet{vanderspek_2018}.
  The noise from unresolved background stars is expected to be more
  important than read noise at the faint end, but is omitted from the
  plot due to model uncertainties (see \S~\ref{subsec:lcstatistics}).
		\label{fig:rms_vs_mag}
	}
\end{figure}
